Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-25 paper.tex
start summary of LONI

    \section{OpenMOLE}
        \subsection{summary}
        OpenMOLE (Open MOdeL Experiment) is a domain agnostic pipelining
framework that focuses on simplifying workflow creation through its Domain
Specific Language (DSL) built on top of Scala. Through the use of its DSL, much
of the backend is abstracted from users. Similarly to other existing pipelining
frameworks, OpenMOLE enables parallelization through plugins, meaning that the
workflow need not be changed between different distribution environments.
Moreover, OpenMOLE supports the deployment of tasks or groups of tasks on different
computing environments.
Another key feature of OpenMOLE is that it attempts to address the
reproducibility issue through the integration of the CARE archiver. CARE allows
for the execution of command-line applications, written in any language, and
attempts to simulate the environment in which the application was designed on.
OpenMOLE also provides embedded methods for parameter exploration.

@@

    \section{LONI}
    \section{Automatic Analysis}
    \section{Dipy, Make, Pydiper} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

    \section{OpenMOLE}
        \subsection{summary}
        OpenMOLE (Open MOdeL Experiment) is a domain agnostic pipelining
framework that focuses on simplifying workflow creation through its Domain
Specific Language (DSL) built on top of Scala. Through the use of its DSL, much
of the backend is abstracted from users. It also offers a GUI for users to build
workflows. Similarly to other existing pipelining
frameworks, OpenMOLE enables parallelization through plugins, meaning that the
workflow need not be changed between different distribution environments.
Moreover, OpenMOLE supports the deployment of tasks or groups of tasks on different
computing environments.
Another key feature of OpenMOLE is that it attempts to address the
reproducibility issue through the integration of the CARE archiver. CARE allows
for the execution of command-line applications, written in any language, and
attempts to simulate the environment in which the application was designed on.
OpenMOLE also provides embedded methods for parameter exploration.

@@

    \section{LONI}
        \subsection{Summary}
        The LONI pipeline processing environment facilitates the development,
sharing and execution of pipelines. Workflow Activities, known as \textit{Modules} in
LONI, are described using Extensible Markup Language (XML), which can easily
shared between user groups. LONI runs on the Java platform, allowing it to be
platform independent and has support DRMAA clusters and symmetric
multiprocessing (SMP) systems. In order to
capture provenance information, LONI is also equipped with a provenance manager.

        \subsection{Pipeline description}
        LONI uses the dataflow programming model to represent the pipeline. Data
flows between \textit{Modules} through \textit{data pipes}. Sub-pipelines are
known and \textit{Pipelets}. Modules are defined by the input arguments/streams
and output arguments/stream. Arguments in LONI may be specific
filetypes, flags or values listed in the order in which the application
requires. The provided arguments may be required or optional and can also be
duplicated, if necessary. List of inputs may also be provided to process
multiple inputs with copies of the same module in parallel (batch processing). Conversely, it is
also possible to group list of inputs so as to process them all by the single
module \note{Need to express this better}. Input/Output arguments may be added
to the table of global variables for easy access throughout the pipeline. It is
possible to apply variable modifiers to the variables stored within the table.   
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Automatic Analysis}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Dipy}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Make}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pydiper}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
